Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-05-03 src/tex/ms.tex
Update

% We believe that either the ansatz does not suit waveforms within certain
% regions of parameter space or the set of optimized coefficients falls to a
% minimum where they do not fit some testing waveforms. If in some region of
% parameter space, the ansatz does not fit well with NR waveforms, it would
% never be able to have consistent improvement under optimization. Instead, it
% would surf around the loss manifold with random fluctuations in mismatches. If
% the set of coefficients does not fit, then dividing the parameter space into
% regions and fitting separate sets of coefficients should give better results.

Given that the waveform model's ansatz may not be entirely compatible with NR,
and the optimization procedure is carried out over a distribution of waveforms
with varying intrinsic parameters, it is conceivable that some trade-offs in
accuracy exist between different parts of the parameter space. If this is the
cause of the high mismatch tail's failure to improve during joint-optimization,
segmenting the parameter space into smaller subspaces should alleviate this
problem. On the other hand, if the ansatz lacks the correct parameterized form
to capture the NR waveforms' behavior as a function of the intrinsic parameters,
the results will always be biased, and we should not expect any improvement,
even if we segment the parameter space during training.

>>>>

% We believe that either the ansatz does not suit waveforms within certain
% regions of parameter space or the set of optimized coefficients falls to a
% minimum where they do not fit some testing waveforms. If in some region of
% parameter space, the ansatz does not fit well with NR waveforms, it would
% never be able to have consistent improvement under optimization. Instead, it
% would surf around the loss manifold with random fluctuations in mismatches. If
% the set of coefficients does not fit, then dividing the parameter space into
% regions and fitting separate sets of coefficients should give better results.
Although most of the waveforms show improvement in figure \ref{fig:q148}, the
high mismatch tail of the distribution remains unaffected. Given that the
waveform model's ansatz may not be entirely compatible with NR, and the
optimization procedure is carried out over a distribution of waveforms with
varying intrinsic parameters, it is conceivable that some trade-offs in accuracy
exist between different parts of the parameter space. If this is the cause of
the lack of improvement in the high mismatch tail of the distribution,
segmenting the parameter space into smaller subspaces should alleviate this
problem. On the other hand, if the ansatz lacks the correct parameterized form
to capture the NR waveforms' behavior as a function of the intrinsic parameters,
the results will always be biased, and we should not expect any improvement,
even if we segment the parameter space during training.
